\chapter{FASTA tools}
\label{fasta}
%Write something about FASTA tools

Current available FASTA tools, for analysis and manipulation, are:
\begin{enumerate}
\item \texttt{goose-fasta2seq}: it converts a FASTA or Multi-FASTA file format to a seq.
\item \texttt{goose-fastaextract}: it extracts sequences from a FASTA file, which the range is defined by the user in the parameters.
\item \texttt{goose-fastaextractbyread}: it extracts sequences from each read in a Multi-FASTA file (splited by \textbackslash n), which the range is defined by the user in the parameters.
\item \texttt{goose-fastainfo}: it shows the readed information of a FASTA or Multi-FASTA file format.
\item \texttt{goose-mutatefasta}: it reates a synthetic mutation of a fasta file given specific rates of editions, deletions and additions.
\item \texttt{goose-randfastaextrachars}: it substitues in the DNA sequence the outside ACGT chars by random ACGT symbols.
\item \texttt{goose-extractreadbypattern}: it extracts reads from a Multi-FASTA file format given a pattern in the header.
\item \texttt{goose-findnpos}: it reports the ''N'' regions in a sequence or FASTA (seq) file.
\item \texttt{goose-seq2fasta}: it converts a genomic sequence to pseudo FASTA file format.
%\item \texttt{goose-permuteseqbyblocks}
\item \texttt{goose-splitreads}: it splits a Multi-FASTA file to multiple FASTA files.
\item \texttt{goose-renamehumanheaders}: it changes the headers of FASTA or Multi-FASTA file to simple chrX by order, where X is the number.
%Incomplete tools
%%\item \texttt{goose-reverselm}%: it reverses the order of a large sequence. Low memory usage for large files.
\end{enumerate}

\input{\FASTAToolsPath/fasta2seq.tex}
\input{\FASTAToolsPath/fastaextract.tex}
\input{\FASTAToolsPath/fastaextractbyread.tex}
\input{\FASTAToolsPath/fastainfo.tex} 
\input{\FASTAToolsPath/mutatefasta.tex}
\input{\FASTAToolsPath/randfastaextrachars.tex}
\input{\FASTAToolsPath/extractreadbypattern.tex}
\input{\FASTAToolsPath/findnpos.tex}
\input{\FASTAToolsPath/seq2fasta.tex}
%\input{\FASTAToolsPath/permuteseqbyblocks.tex}
\input{\FASTAToolsPath/splitreads.tex}
\input{\FASTAToolsPath/renamehumanheaders.tex}


%Incomplete tools
%%\input{\FASTAToolsPath/reverselm.tex}