\chapter{FASTQ tools}
\label{fastq}

Current available tools for FASTQ format analysis and manipulation include:
\begin{enumerate}

\item \texttt{goose-fastq2fasta}: it converts a FASTQ file format to a pseudo FASTA file.
\item \texttt{goose-fastq2mfasta}: it converts a FASTQ file format to a pseudo Multi-FASTA file.
%\item \texttt{goose-fastqclustreads}
\item \texttt{goose-FastqExcludeN}: it discards the FASTQ reads with the minimum number of "N" symbols.
\item \texttt{goose-FastqExtractQualityScores}: it extracts all the quality-scores from FASTQ reads.
\item \texttt{goose-FastqInfo}: it analyses the basic informations of FASTQ file format.
\item \texttt{goose-FastqMaximumReadSize}: it filters the FASTQ reads with the length higher than the value defined.
%\item \texttt{goose-FastqMinimumLocalQualityScoreForward}
%\item \texttt{goose-FastqMinimumLocalQualityScoreReverse}
\item \texttt{goose-FastqMinimumQualityScore}: it discards reads with average quality-score below of the defined.
\item \texttt{goose-FastqMinimumReadSize}: it filters the FASTQ reads with the length smaller than the value defined.
%\item \texttt{goose-fastqpack}
%\item \texttt{goose-fastqsimulation}
%\item \texttt{goose-FastqSplit}
%\item \texttt{goose-fastqunpack}
%\item \texttt{goose-randfastqextrachars}
\item \texttt{goose-seq2fastq}: it converts a genomic sequence to pseudo FASTQ file format.
\item \texttt{goose-mutatefastq}: it creates a synthetic mutation of a FASTQ file given specific rates of mutations, deletions and additions.

%Check if theses ones are in the right chapter
%\item \texttt{goose-getunique}
%\item \texttt{goose-mfmotifcoords}
%\item \texttt{goose-newlineonnewx}
%\item \texttt{goose-period}
%\item \texttt{goose-real2binthreshold}
%\item \texttt{goose-reducematrixbythreshold}
%\item \texttt{goose-renamehumanheaders}
%\item \texttt{goose-searchphash}
%\item \texttt{goose-SequenceToGroupSequence}


%Incomplete tools
%\item \texttt{goose-FastqTrimm}

\end{enumerate}

%TO DO
\input{\FASTQToolsPath/fastq2fasta.tex}
\input{\FASTQToolsPath/fastq2mfasta.tex}
%\input{\FASTQToolsPath/fastqclustreads.tex}
\input{\FASTQToolsPath/FastqExcludeN.tex}
\input{\FASTQToolsPath/FastqExtractQualityScores.tex}
\input{\FASTQToolsPath/FastqInfo.tex}
\input{\FASTQToolsPath/FastqMaximumReadSize.tex}
%\input{\FASTQToolsPath/FastqMinimumLocalQualityScoreForward.tex}
%\input{\FASTQToolsPath/FastqMinimumLocalQualityScoreReverse.tex}
\input{\FASTQToolsPath/FastqMinimumQualityScore.tex}
\input{\FASTQToolsPath/FastqMinimumReadSize.tex}
%\input{\FASTQToolsPath/fastqpack.tex}
%\input{\FASTQToolsPath/fastqsimulation.tex}
%\input{\FASTQToolsPath/FastqSplit.tex}

%\input{\FASTQToolsPath/fastqunpack.tex}
%\input{\FASTQToolsPath/getunique.tex}
%\input{\FASTQToolsPath/mfmotifcoords.tex}
\input{\FASTQToolsPath/mutatefastq.tex}
%\input{\FASTQToolsPath/newlineonnewx.tex}
%\input{\FASTQToolsPath/period.tex}
%\input{\FASTQToolsPath/randfastqextrachars.tex}
%\input{\FASTQToolsPath/real2binthreshold.tex}
%\input{\FASTQToolsPath/reducematrixbythreshold.tex}
%\input{\FASTQToolsPath/renamehumanheaders.tex}
%\input{\FASTQToolsPath/searchphash.tex}
\input{\FASTQToolsPath/seq2fastq.tex}
%\input{\FASTQToolsPath/SequenceToGroupSequence.tex}

%Incomplete tools
%%\input{\FASTQToolsPath/FastqTrimm.tex}